Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-12 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Extra calculations for AUDPStairs added, updated for all trials

#### AUDPC curve
```{r King11_AUDPC}
Goolhi_13_dat <- cbind(Goolhi_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,16,33)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c(1,16,33)
                                        )
                          )

@@

Goolhi_13_m <- Goolhi_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              #disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Goolhi_13_m, 
                            new_data_column = "AUDPC_m", 
                            ignore_columns = c(5:10,30:46))

PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Goolhi_13_m, 
                            new_data_column = "AUDPC_sd", 
                            ignore_columns = c(5:10,30:46))

@@

MarysM_13_dat <- cbind(MarysM_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,12,12+19)
                                        )
                          )
```

#### Calculating the treatment means
```{r Marys_means}
MarysM_13_m <- MarysM_13_dat %>%
   group_by(n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = MarysM_13_m, 
                            new_data_column = "AUDPC_m", 
                            ignore_columns = c(5:10,30:46))

PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = MarysM_13_m, 
                            new_data_column = "AUDPC_sd", 
                            ignore_columns = c(5:10,30:46))

@@

Premer_13_dat <- cbind(Premer_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   Premer_13[,c("Inc_31D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
                                                  12+19)
                                        )
                          )

@@

#### Calculating the treatment means
```{r Prem13_TreatmentMeans}
Premer_13_m <- Premer_13_dat %>%
   group_by(n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
            plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Premer_13_m, 
                            new_data_column = "AUDPC_m", 
                            ignore_columns = c(5:10,30:46))

PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Premer_13_m, 
                            new_data_column = "AUDPC_sd", 
                            ignore_columns = c(5:10,30:46))

@@

Millm_13_dat <- cbind(Millm_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   Millm_13[,c("Inc_23D","Inc_42D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,23,42)
                                        )
                          )
```

#### Calculating the treatment means
```{r Millm13_TreatmentMeans}
Millm_13_m <- Millm_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = NA,
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Millm_13_m, 
                            new_data_column = "AUDPC_m", 
                            ignore_columns = c(5:10,30:46))

PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Millm_13_m, 
                            new_data_column = "AUDPC_sd", 
                            ignore_columns = c(5:10,30:46))

@@

Herm_15_dat <- 
   data.frame(trial_ref = "mung1415/01",
              year = "2015",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_15_dat$Rep,
              planting_date = as.Date("2015-01-19", format = "%Y-%m-%d"),
              emergence_date = as.Date("2015-01-24", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2015-03-16", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_15_dat$trade_name),
              fungicide_ai = Herm_15_dat$fungicide_ai,
              dose_ai.ha = Herm_15_dat$dose_ai.ha,
              n_treatment = as.numeric(Herm_15_dat$n_treatment),
              fungicide_application_1 = Herm_15_dat$fungicide_application_1,
              fungicide_application_2 = Herm_15_dat$fungicide_application_2,
              fungicide_application_3 = Herm_15_dat$fungicide_application_3,
              total_fungicide = Herm_15_dat$spray_n,
              harvest_date = as.Date("2015-04-20", format = "%Y-%m-%d"),
              final_assessment = as.Date("2015-04-06", format = "%Y-%m-%d"),
              PM_final_severity = Herm_15_dat$day22,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_15_dat$`Plot.Yield.(t/ha)`),
              AUDPC = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
                            FUN = audpc, dates = c(0,1,8,15,22)),# -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              stringsAsFactors = FALSE)

@@

#### Calculating treatment means
```{r Herm15_means}
Herm_15_m <- Herm_15_dat %>%
   group_by(host_genotype, n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Herm_15_m, 
                            new_data_column = "AUDPC_m", 
                            ignore_columns = c(5:10,30:46))

PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Herm_15_m, 
                            new_data_column = "AUDPC_sd", 
                            ignore_columns = c(5:10,30:46))

@@

# Mean Disease incidence assessments through the 2016 season
Herm_16.DR  <-
   read.xlsx(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/2016 Mungbean PM trials summary.xlsx",
      sheet = "Hermitage_2016",
      startRow = 5,
      colNames = TRUE
   )
names(Herm_16.DR)[1:6] <- c("Treatment", "dae24","dae38","dae48","dae63","Final_Yield_tHa")
names(Herm_16.DR)[6] <- "Final_Yield_tHa"
Herm_16.DR$n_treatment <- c(4,3,7,5,2,6,1)

>>>>

#### AUDPC curve
```{r Goolhi13_AUDPC}
Goolhi_13_dat <- cbind(Goolhi_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,16,33)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c(1,16,33)
                                        )
                          )

@@

Goolhi_13_m <- Goolhi_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              #disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             AUDPS_m = mean(AUDPS),
             AUDPS_sd = sd(AUDPS),
             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
                               data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3],
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Goolhi_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

#### AUDPC curve
```{r Mary13_AUDPC}
MarysM_13_dat <- cbind(MarysM_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,12,12+19)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c(1,12,12+19)
                                        )
                          )

#### Calculating the treatment means
```{r Marys_means}
MarysM_13_m <- MarysM_13_dat %>%
   group_by(n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             AUDPS_m = mean(AUDPS),
             AUDPS_sd = sd(AUDPS),
             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
                               data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3],
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]
             )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = MarysM_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

@@

#### AUDPC curve
```{r Prem13_AUDPC}
Premer_13_dat <- cbind(Premer_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                           Premer_13[,c("Inc_31D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
                                                  12+19)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                           Premer_13[,c("Inc_31D")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
                                                  12+19)
                                        )
                          )

#### Calculating the treatment means
```{r Prem13_TreatmentMeans}
Premer_13_m <- Premer_13_dat %>%
   group_by(n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
            plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
            AUDPS_m = mean(AUDPS),
             AUDPS_sd = sd(AUDPS),
             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
                               data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3],
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Premer_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

#### AUDPC curve
```{r Mill13_AUDPC}
Millm_13_dat <- cbind(Millm_13_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                           Millm_13[,c("Inc_23D","Inc_42D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,23,42)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                           Millm_13[,c("Inc_23D","Inc_42D")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c(1,23,42)
                                        )
                          )

#### Calculating the treatment means
```{r Millm13_TreatmentMeans}
Millm_13_m <- Millm_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = NA,
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             AUDPS_m = mean(AUDPS),
             AUDPS_sd = sd(AUDPS),
             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
                               data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3],
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3]
             )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Millm_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

Herm_15_dat <- 
   data.frame(trial_ref = "mung1415/01",
              year = "2015",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_15_dat$Rep,
              planting_date = as.Date("2015-01-19", format = "%Y-%m-%d"),
              emergence_date = as.Date("2015-01-24", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2015-03-16", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_15_dat$trade_name),
              fungicide_ai = Herm_15_dat$fungicide_ai,
              dose_ai.ha = Herm_15_dat$dose_ai.ha,
              n_treatment = as.numeric(Herm_15_dat$n_treatment),
              fungicide_application_1 = Herm_15_dat$fungicide_application_1,
              fungicide_application_2 = Herm_15_dat$fungicide_application_2,
              fungicide_application_3 = Herm_15_dat$fungicide_application_3,
              total_fungicide = Herm_15_dat$spray_n,
              harvest_date = as.Date("2015-04-20", format = "%Y-%m-%d"),
              final_assessment = as.Date("2015-04-06", format = "%Y-%m-%d"),
              PM_final_severity = Herm_15_dat$day22,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_15_dat$`Plot.Yield.(t/ha)`),
              AUDPC = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
                            FUN = audpc, 
                            dates = c(0,1,8,15,22)),
              # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              AUDPS = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
                            FUN = audps, 
                            dates = c(0,1,8,15,22)),
              stringsAsFactors = FALSE)

@@

#### Calculating treatment means
```{r Herm15_means}
Herm_15_m <- Herm_15_dat %>%
   group_by(host_genotype, n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             AUDPS_m = mean(AUDPS),
             AUDPS_sd = sd(AUDPS),
             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
                               data = Herm_15_dat))[1,3],
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                data = Herm_15_dat))[1,3]
   )

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Herm_15_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

#### Mean disease incidence data
```{r}
Herm_16.DR  <-
   read.xlsx(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/2016 Mungbean PM trials summary.xlsx",
      sheet = "Hermitage_2016",
      startRow = 5,
      colNames = TRUE
   )
names(Herm_16.DR)[1:6] <- c("Treatment", "dae24","dae38","dae48","dae63","Final_Yield_tHa")
